\section*{Appended papers}
\textbf{Paper A}\\
Luca Di Stasio, Zoubir Ayadi (2019). Finite Element solution of the fiber/matrix interface crack problem: convergence properties and mode mixity of the Virtual Crack Closure Technique. \textit{Finite Elements in Analysis and Design}, 167, 103332.\\[10pt]
\textbf{Paper B}\\
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Energy release rate of the fiber/matrix interface crack in UD composites under transverse loading: effect of the fiber volume fraction and of the distance to the free surface and to non-adjacent debonds. \textit{Theoretical and Applied Fracture Mechanics}, 103, 102251.\\[10pt]
\textbf{Paper C}\\
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Effect of the proximity to the $0^{\circ}/90^{\circ}$ interface on Energy Release Rate of fiber/matrix interface crack growth in the  $90^{\circ}$-ply of a cross-ply laminate under tensile loading. Submitted to \textit{Journal of Composite Materials}.\\[10pt]
\textbf{Paper D}\\
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Growth of interface cracks on consecutive fibers: on the same or on the opposite sides? Submitted to \textit{Proceedings of the 12$^{th}$ International Conference on Composite Science and Technology (ICCST 12)}, in: \textit{Materials Today: Proceedings}.\\[10pt]
\textbf{Paper E}\\
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Estimating the average size of fiber/matrix interface cracks in UD and cross-ply laminates. \textit{Proceedings of the $7^{th}$ ECCOMAS Thematic Conference on the Mechanical Response of Composites}.\\

\newpage

\section*{Other relevant contributions}
\textbf{Peer-reviewed journal publications}\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Formation of transverse cracks from the growth of multiple adjacent debonds on consecutive fibers in UD composites under transverse tension: Effect of the mutual position of debonds on Energy Release Rate. To be submitted to \textit{Applied Composite Materials}, special issue for the \textit{12$^{th}$ International Conference on Composite Science and Technology (ICCST 12)}.\\[12.5pt]
\textbf{Conference proceedings}\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2018). Effect of boundary conditions on microdamage initiation in thin ply composite laminates \textit{Proceedings of the 18$^{th}$ European Conference on Composite Materials (ECCM18)}.\\[12.5pt]
\textbf{Conference contributions (oral)}\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Estimating the average size of fiber/matrix interface cracks in UD and cross-ply laminates. $7^{th}$ ECCOMAS Thematic Conference on the Mechanical Response of Composites - September 18-20, 2019 - Girona, Spain.\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Ply-thickness effect on fiber-matrix interface crack growth. $9^{th}$ International Conference on Composite Testing and Model Identification (COMPTEST2019) - May 27-29, 2019 - Lule\aa, Sweden.\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Growth of interface cracks on consecutive fibers: on the same or on the opposite sides? $12^{th}$ International Conference on Composite Science and Technology (ICCST12) - May 8-10, 2019 - Sorrento, Italy.\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2019). Investigation of scaling laws of the fiber/matrix interface crack in polymer composites through finite element-based micromechanical modeling. $10^{th}$ EEIGM International Conference on Advanced Materials Research - April 25-26, 2019 - Moscow, Russia.\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2018). Effect of boundary conditions on microdamage initiation in thin ply composite laminates. $18^{th}$ European Conference on Composite Materials (ECCM18) - June 24-28, 2018 - Athens, Greece.\\[10pt]
Luca Di Stasio, Janis Varna, Zoubir Ayadi (2017). Micromechanical modeling of thin ply effects on microdamage in Fiber Reinforced Composite laminates. International Materials Research Meeting of the Greater Region (IMRM) - April 6-7, 2017 - Saarbr\"ucken, Germany.
